D3064R0: OOTA Execution on Real Implementations is Provably Vacuous

### 2023-12-29 ootavacuous.tex
Non-unitary semantic dependencies
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

>>>>

Worse yet, suppose that both \co{y} and \co{z} are zero.
Then there is no semantic dependency from either to \co{x} unless both
\co{y} and \co{z} change.
Alternatively, when both \co{y} and \co{z} are zero, there is no semantic
dependency from either \co{y} or \co{z} to \co{x}, but rather a semantic
dependency from the combination of \co{y} and \co{z} to \co{x}.
This means that precise definitions of sdep cannot always rely on
single-variable perturbations.
